% Will_Dignazio.tex
%
% (c) 2002 Matthew Boedicker <mboedick@mboedick.org> (original author) http://mboedick.org
% (c) 2003 David J. Grant <dgrant@ieee.org> http://www.davidgrant.ca
% (c) 2007 Todd C. Miller <Todd.Miller@courtesan.com> http://www.courtesan.com/todd
% (c) 2009 Derek R. Hildreth <derek@derekhildreth.com> http://www.derekhildreth.com 
% (c) 2012 William M. Ziener-Dignazio <slackwill@csh.rit.edu> http://csh.rit.edu/~slackwill
%
%This work is licensed under the Creative Commons Attribution-NonCommercial-ShareAlike License. To view a copy of this license, visit http://creativecommons.org/licenses/by-nc-sa/1.0/ or send a letter to Creative Commons, 559 Nathan Abbott Way, Stanford, California 94305, USA.

% GENERAL NOTE:  There may be some notes specific to myself.  If you're only interested in my LaTeX source or it doesn't make sense, please disregard it.

\documentclass[letterpaper,11pt]{article}

%-----------------------------------------------------------
\usepackage{tabularx}
\usepackage{latexsym}
\usepackage{fullpage}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage[pdftex]{hyperref}
\hypersetup{
    colorlinks,%
    citecolor=black,%
    filecolor=black,%
    linkcolor=black,%
    urlcolor=mygreylink     % can put red here to visualize the links 
}
\urlstyle{same}
\definecolor{mygrey}{gray}{.85}
\definecolor{mygreylink}{gray}{.30}
\textheight=9.0in
\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Adjust margins
\addtolength{\oddsidemargin}{-0.375in}
\addtolength{\evensidemargin}{0.375in}
\addtolength{\textwidth}{0.5in}
\addtolength{\topmargin}{-.375in}
\addtolength{\textheight}{0.75in}

%-----------------------------------------------------------
%Custom commands
\newcommand{\resitem}[1]{\item #1 \vspace{-2pt}}
\newcommand{\resheading}[1]{{\large \colorbox{mygrey}{\begin{minipage}{\textwidth}{\textbf{#1 \vphantom{p\^{E}}}}\end{minipage}}}}
\newcommand{\restwoheading}[2]{{\large \colorbox{mygrey}{\begin{minipage}{\textwidth}{\textbf{#1 \vphantom{p\^{E}}}}\end{minipage}}}}
\newcommand{\ressubheading}[4]{
\begin{tabular*}{6.5in}{l@{\extracolsep{\fill}}r}
		\textbf{#1} & #2 \\
		{#3} & {#4} \\
\end{tabular*}\vspace{-6pt}}
\newcommand{\restwosubheading}[2]{
\begin{tabular*}{6.5in}{l@{\extracolsep{\fill}}r}
		\textbf{#1} & #2 \\
\end{tabular*}\vspace{-6pt}}
%-----------------------------------------------------------

%-----------------------------------------------------------
%General Resume Tips
%   No periods!  Technically, nothing in this document is a full sentence.
%   Use parallelism by ending key words with the same thing,  i.e. "Coordinated; Designed; Communicated".
%   More tips on bottom of this LaTeX document.
%-----------------------------------------------------------

\begin{document} 

\thispagestyle{empty}
\pagestyle{empty}

\newcommand{\mywebheader}{
\begin{tabular*}{7in}{l@{\extracolsep{\fill}}r} \\
	\textbf{\href{http://www.willdignazio.com/}{\large William M. Dignazio}} & \href{mailto:wdignazio@gmail.com}{wdignazio@gmail.com}\\ &
	\href{http://willdignazio.com/}{willdignazio.com} \\ \vspace{-10mm} \\
	{\footnotesize {{Current: 1535 South Ave,
Rochester, NY 14620}}} & \\
	{\footnotesize {{Home: 1650 Warrendale Bayne Rd, Baden, PA 15005}}} & \\
	{\footnotesize {{Phone: (724) 831-7693}}} 	\end{tabular*}
\\
\vspace{0.1in}}

% CHANGE HEADER SOURCE HERE
\mywebheader

%%%%%%%%%%%%%%%%%%%%%%
\resheading{Objective}
{
	\footnotesize
	\begin{itemize}
		\item{Obtain a cooperative study for a minimum of 3 months}
		\item{A position of Software Engineer or equivalent}
		\item{To research, design, and implement solutions for real world problems}
	\end{itemize}
}
%%%%%%%%%%%%%%%%%%%%%%
\resheading{Education}
	{ \footnotesize
	\begin{itemize}
		\item
			\ressubheading{Rochester Institute of Technology - New York}{\href{http://www.rit.edu}{rit.edu}}{\href{http://www.cs.rit.edu/}{Undergraduate Computer Science Student}}{Aug. 2011 - Present}
				{ \footnotesize
				\begin{itemize}
					\item{Expected Graduation Date: June 2016}
					\item{Core Courses:}
						\begin{itemize}
							\item{Computer Organization}
							\item{Computer Science[1-4]}
							\item{Concepts of Parallel \& Distributed Systems}
							\item{Data Communications}
						\end{itemize}
				\end{itemize}
				}
	\end{itemize} % End Education list
	}
%%%%%%%%%%%%%%%%%%%%%%

\resheading{{Skills}}
{ \footnotesize
		\begin{itemize}
			\item{Languages: Assembly (x86, MIPS), C, Java, Julia, Python}
			\item{Tools: Autotools, CMake/Make, Emacs, Git, LaTex, Subversion, Vi/Vim}
			\item{Concepts: Lockless Design, Parallel \& Distributed Systems, Systems Programming}
		\end{itemize}
}
%%%%%%%%%%%%%%%%%%%%%%
\resheading{Professional Experience}
{\footnotesize
	\begin{itemize}
			\item
			\ressubheading{Exablox}{\href{http://www.exablox.com/}{exablox.com}}{File System Performance Intern}{June 2013 - January 2014}
			{ \footnotesize
				\begin{itemize}
					\item{Tuned and optimized our object-based file system}
					\item{Researched and worked on lockless hash table implementation}
					\item{Worked with various FUSE based mechanisms and third party libraries}
					\item{Developed Octeon hardware interfaces for our file system}
					\item{Rendered statistics and generated benchmark marketing data}
				\end{itemize}
			}
			\item 
			\ressubheading{Information and Technology Services}{\href{http://www.rit.edu/its/}{rit.edu/its}}{Infrastructure Engineer}{June 2012 - January 2013}
			{ \footnotesize
				\begin{itemize}
					\item{Handled software maintenance and feature tickets for in house applications}
					\item{Dealt with critical data, and university requirements}
				\end{itemize}
			}
		\item	
			\ressubheading{Newstex}{\href{http://www.newstex.com/}{newstex.com}}{Web Programmer}{March - May 2012} 
				{ \footnotesize 
				\begin{itemize}
					\item{Worked with cloud applications, including Boto and Botoweb.}
					\item{Designed and implemented data mining utilities for LinkedIn, Google Plus, and Twitter.}
				\end{itemize}
				}
		\item 
			\ressubheading{Computer Science House}{\href{http://www.csh.rit.edu/}{csh.rit.edu}}{Systems Administrator}{Active Member} 
			{ \footnotesize
				\begin{itemize}		
					\resitem{Operations and Communications Director (Head SysAdmin)}
					\resitem{Yearly technical Major Project}
				\end{itemize}
			}		
	\end{itemize}  % End Experience list
}
%%%%%%%%%%%%%%%%%%%%%%

\resheading{Online Presence}
{
	\begin{tabularx}{2in}{XX}
		LinkedIn: & \href{http://www.linkedin.com/in/slackwill/}{linkedin.com/in/slackwill} \\
		Githhub: & \href{http://www.github.com/WillDignazio}{github.com/WillDignazio} \\
		Blog: & \href{http://www.willdignazio.com/}{willdignazio.com} \\
		Twitter: & \href{https://twitter.com/WillDignazio}{twitter.com/WillDignazio} \\
	\end{tabularx}
}
\pagebreak

%%%%%%%%%%%%%%%%%%%%%%
\resheading{Projects}
{ \footnotesize
	\textit{Available on {\href{http://www.github.com/WillDignazio/}{github.com/WillDignazio.}}}
	\begin{itemize}
		\item 
		\restwosubheading{SOS (Sandbox Operating System) }{C}
			\begin{itemize}
				\item{Open Source Kernel: Formally called "Foundation", it is a microkernel built off the specs provided by the Intel x86 Architecture manuals, and various online wikis.}
				\item{Most hardware will support the system, being that its native architecture is x86. Recent design changes that have yet to be implemented allow portability to other architectures, such as ARM.}
			\end{itemize}
		\item		
		\restwosubheading{Atlas}{Assembly}
			\begin{itemize}
				\item{Intel Architecture bootstrap binary, boot arbitrary C or C++ code linked against it. Allows for quick system development, and simple x86 embedded device coding.} 
				\item{Supports 16 and 32 bit operation, features simple graphics library for debugging and standard output.}
			\end{itemize}
		\item
		\restwosubheading{slackbot}{C}
			\begin{itemize}
				\item{A virtual bot designed to administrate our IRC channels, giving the proper users automatic administrative access, and guests restricted access.}
				\item{Integrates with LDAP to identify users, as well as connects and operates over SSL for secure authentication and data gathering.}
			\end{itemize}
		\item		
		\restwosubheading{asmblog}{Assembly}
			\begin{itemize}
				\item{Blog platform written in NASM (Netwide Assembly, designed for use on 64-bit x86 operating systems.)}
				\item{Uses FCGI and and custom routines to serve web content, can be used in tandem with any web server, my server hosts a build of asmblog with the NGINX web server.}
			\end{itemize}
		\item
		\restwosubheading{PAGEFAULT}{Printed Content}
			\begin{itemize}
				\item{Floor research and development journal, focusing on member project development and design.}
				\item{Posted on a bi-weekly basis, with regular submissions, averaging 3 posts per release.}
			\end{itemize}
	\end{itemize}
}

%%%%%%%%%%%%%%%%%%%%%%

\end{document}


%%%%%%%%%%%%%%%%%%%%%%%%
% GENERAL RESUME NOTES %
%%%%%%%%%%%%%%%%%%%%%%%%
Need to brush up on the skills section?  Here are some really good ideas:

- Communication: The ability to express and interpret ideas and convey knowledge. 
Skills like speaking effectively, writing concisely, listening attentively, expressing ideas, 
reporting information, editing, interviewing, and facilitating group discussion. 
 
- Research and Planning: The ability to search for specific knowledge and formulate a 
program for a definite course of action. Skills like forecasting, predicting, identifying 
issues, finding alternatives, gathering information, solving problems, setting goals, 
extracting information, and developing strategies. 
 
- Human Relations: The ability to apply interpersonal skills to resolve conflict, relate to 
people, and help people. Skills like providing support for others, listening, delegating 
with respect, representing others, asserting, developing rapport, and perceiving 
feelings. 
 
- Management, Organization, Leadership: The ability to supervise others and guide 
individuals and groups towards the completion of tasks. Skills like managing groups, 
selling ideas, making decisions, managing conflict, coordinating tasks, teaching, 
enlisting help. 

Source: 
http://www.squawkfox.com/2009/03/08/6-action-words-that-make-your-resume-rock/

Other Resources: 
http://www.tvmier.com/Resume_Education.html
